Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-19 Grassmannian_cells.tex
continued improving section 5

The representation $\tilde P_3$ is given by the quiver
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{\alpha_n}[llu]}
        \end{align*}
	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.  Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.  The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&(2,\alpha_{j_1}^{-1})\ar_{\alpha_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_{j_l}^{-1})\ar_{\alpha_{j_l}}[llu]}
        \end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=\alpha^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,\alpha_{j_i}^{-1})\xrightarrow{\alpha_{j_i}}(1,1)$ for $i=1,\ldots,l$.

@@

The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians. Therefore, we use the recursive construction described in Section \ref{Lifting}. In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering. Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and on $\udim P_m^V$.

Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where $P_2^{(n-1)}$ is chosen to be the cokernel of the short exact sequence
\[
  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}.}
\]
Without loss of generality, we make the following choice when defining
\[
  P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{\alpha_1}i^{(n-1)}_2%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
\]
by its coefficient quiver.
Denoting by $j_1$ the single vertex of the coefficient quiver of $P_1$, we have 
\[
  \Ext(P_2^{(n-1)},P_1)=\langle i^{(n-1)}_{2}\xrightarrow{v_l}j_1\mid l=2,\ldots,n\rangle.
\]

This defines recursively the representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ when considering the short exact sequences
\[\ses{P_1}{P_2^{(k)}}{P_2^{(k+1)}}\]
by the coefficient quivers
\begin{align}
  \label{coeff}\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.
\end{align}
Note that we have a short exact sequence
\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
We define the $2$-quiver of $P_2^{(k)}$ by
\\

\begin{tikzpicture}
\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
\draw (0,0) node (A) {$j^{(k)}_{2,n-k}$} +(2.5,0) node (B) {$j^{(k)}_{2,n-k-1}$}+(2.5,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(5,0) node (B1) {$\dots$} +(7.5,0) node (C) {$j^{(k)}_{2,2}$} +(7.5,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(10,0) node (D) {$j^{(k)}_{2,1}$}  +(12.5,0) node (E) {$i^{(k)}_2$} +(10,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
\draw[<-] (D)--(E) node[pos=.5,above] {$v_1$};
\draw[->,red] (Q1)--(C) node[pos=.5,above] {$v_2$};
\draw[->,red] (Q2)--(B1) node[pos=.5,above] {$v_3$};
\draw[->,red] (Q2b)--(B) node[pos=.5,above] {$v_{n-k-1}$};

\draw[->,red] (Q3)--(A) node[pos=.5,above] {$v_{n-k}$};
\end{tikzpicture}
\\

\noindent
where the $2$-arrows are coloured red. As the number of strong successor closed subsets of this $2$-quiver coincides with the number of successor closed subsets of the coefficient quiver, for clearness reasons, we will mostly work with the coefficient quiver instead.

The next step is to define the $2$-quivers of $P^{(k)}_3$ whence the remaining $2$-quivers can be obtained recursively. First we choose the basis of $\Ext(P_2^{(1)},P_2)$ given by the linear maps
$$\{i_2^{(n-1)}\xlongrightarrow{v_n}j_{2,i}\mid i=n-1,\ldots,1\}.$$
This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ where we drop the indices of the vertices in abuse of notation.
\\

\begin{tikzpicture}[scale=1.4]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$v_2$};
\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{(1)}$} ; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$v_2$};
\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

@@

\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{(n-3)}$} ; 
\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$v_{n-2}$};
\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{(n-2)}$}; 
\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$v_2$};
\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{(n-1)}$}   ; 
\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $v_1$};
\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $v_2$};
\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $v_{n-1}$};
%\tikzstyle{every node}=[circle,fill=white!10]
\node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
%\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$v_{n}$};
\node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$v_{n}$};
\node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$v_{n}$};
\node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};

\node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$v_{n}$};
\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$v_{n}$};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$v_{n}$};

@@

We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$. If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, Lemma \ref{AR} gives a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$. Let us consider the case $m=3$. The coefficient quiver of $\tau P_3^{(k)}$ is given by
\[\xymatrix@R10pt@C20pt{&&i_{1}\ar_{v_1}[lld]\\ j &&\vdots\\&&i_{k}\ar_{v_{k}}[llu]}.\]
The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{v_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{v_l} i_l$. Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{(k)}$ to the image of the corresponding homomorphism $P_2\to P_1^{(k)}$ which is of dimension $(1,1)$. In the above illustration, we forgo to insert the corresponding rectangles and just connected the $2$-arrows to the sinks of the corresponding subquivers. It can be seen that this is no restriction from the combinatorial point of view.

Now we can recursively the $2$-quivers of $P_m^{(k)}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating this procedure. For $m\geq 4$, the truncated preprojective $\tau P_m^{(k)}$ can uniquely be found as a quotient of $P_m$.
Recall that we have $\udim P_m^{(k)}=\udim P_{m-1}^{(1)}+(n-k-1)\udim P_{m-1}$. Moreover, we have 
\[\dim \Hom(P_{m-1},\tau P_m^{(1)})=\dim\Ext(P_m^{(1)},P_{m-1})=n-1.\]

@@

\begin{tikzpicture}[scale=1]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
\draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
\draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
\node (Q0)[draw=black,fit={(I3) (J31) }]{};
\node (Q1)[draw=black,fit={(Q0) (J33)}]{};
\node (Q2)[draw=black,fit={(Q1) (I2) (J21) (J22) (J23)}]{};

@@

\draw (0,-4) node (I1b) {$\bullet$} +(1,1) node (J11b) {$\bullet$} +(1,0) node (J12b) {$\bullet$} +(1,-1) node (J13b) {$\bullet$}; 
\draw[->] (I1b)--(J11b) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I1b)--(J12b) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I1b)--(J13b) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

>>>>

The representation $\tilde P_3$ is given by the quiver
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{\alpha_1}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{\alpha_n}[llu]}
        \end{align*}
	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.  Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one. We assume that $(j_1,\ldots,j_l)=(1,\ldots,l)$ which is no restriction as the general case can be obtained by relabelling. 
The Auslander-Reiten translate $\tau\tilde P_{3}^{(1,\ldots,l)}$ is given by
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&(2,\alpha_{l+1}^{-1})\ar_{\alpha_{l+1}}[lld]\\(1,1) &&\vdots\\&&(2,\alpha_{n}^{-1})\ar_{\alpha_{n}}[llu]}
        \end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,i}=\alpha^{-1}_i.\tilde P_2\to\tau\tilde P_{3}^{(1,\ldots,l)}$ has image $(2,\alpha_{i}^{-1})\xrightarrow{\alpha_{i}}(1,1)$ for $i=l+1,\ldots,n$.

@@

The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians. Therefore, we use the recursive construction described in Section \ref{Lifting}. In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering. Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.

Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where we define $P_2^{(n-1)}$ by the lift (using the conventions of Example \ref{smallm}):
\[
  \tilde P_2^{(n-1)}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
\]

%In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
%\[
%  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}.
%\]
Choosing the lifts of $P_1$ supported at $(1,\alpha_2),\ldots,(1,\alpha_n)$, we have 
\[
  \Ext(P_2^{(n-1)},P_1)\cong\langle (2,1)\xrightarrow{\alpha_l}(1,\alpha_l)\mid l=2,\ldots,n\rangle.
\]

This defines recursively the truncated preprojective representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ by the lifts 
\begin{align}
  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
\end{align}
Note that we have a short exact sequence
\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
We define the $2$-quiver of $P_2^{(k)}$ by
\\

\begin{tikzpicture}
\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
\draw[<-] (D)--(E) node[pos=.5,above] {\footnotesize$\alpha_1$};
\draw[->,red] (Q1)--(C) node[pos=.5,above] {\footnotesize$\alpha_2$};
\draw[->,red] (Q2)--(B1) node[pos=.5,above] {\footnotesize$\alpha_3$};
\draw[->,red] (Q2b)--(B) node[pos=.5,above] {\footnotesize$\alpha_{n-k-1}$};

\draw[->,red] (Q3)--(A) node[pos=.5,above] {\footnotesize$\alpha_{n-k}$};
\end{tikzpicture}
\\

\noindent
where the $2$-arrows are coloured red. This $2$-quiver is clearly equivalent to the quiver (\ref{coeff}). For clearness reasons, we will mostly work with the quiver instead.

The next step is to define the $2$-quivers of certain truncated preprojectives $P^{(k)}_3$ whence the remaining $2$-quivers attached to truncated preprojectives $P_m^{(k)}$ can be obtained recursively. In view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any truncated preprojective of this dimension.

As in Section \ref{Lifting}, let $\tilde P_2$ be supported at $(2,1)$. Then we have 
$$\Ext(P_2^{(1)},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_2^{(1)},\alpha_i^{-1}\alpha_n\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_2^{(1)},P_2)$, each basis element given by the linear map $$(2,1)\xlongrightarrow{\alpha_n}(1,\alpha_n)\in\Hom_{\CC}((\tilde P_2^{(1)})_{(2,1)}),(\alpha_i^{-1}\alpha_n\tilde P_2)_{(1,\alpha_n)})$$
for $i=1,\ldots,n-1$.

Now define $\tilde P_3^{(n-1)}:=\tilde P_2^{(1)}$

This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation. Note that the middle vertex of $P_3^{(n-1)}$ is $(2,1)$ and that all $2$-arrows end in a vertex corresponding to the vertex $(1,\alpha_n)$ of $\widetilde{K(n)}$.\\

\begin{tikzpicture}[scale=1.4]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{(1)}$} ; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{(n-3)}$} ; 
\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-2}$};
\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{(n-2)}$}; 
\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{(n-1)}$}   ; 
\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $\alpha_2$};
\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $\alpha_{n-1}$};
%\tikzstyle{every node}=[circle,fill=white!10]
\node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
%\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$\alpha_{n}$};
\node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$\alpha_{n}$};
\node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$\alpha_{n}$};
\node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};

\node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$\alpha_{n}$};
\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$\alpha_{n}$};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$\alpha_{n}$};

@@

We have $\dim \Hom(P_{m-1},\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_{m-1})=n-k$. If a basis of $\Ext(P_m^{(k)},P_{m-1})$ is compatible with a lift to the universal covering,  there is a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{(k)})$. For $m=3$, the lift of $\tau P_3^{(k)}$ is given by 
\[\xymatrix@R10pt@C20pt{&&(2,\alpha_1^{-1})\ar_{\alpha_1}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_k^{-1})\ar_{\alpha_{k}}[llu]}.\]
The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{\alpha_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{\alpha_l} i_l$. Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{(k)}$ to the image of the corresponding homomorphism $P_2\to P_1^{(k)}$ which is of dimension $(1,1)$. In the above illustration, we forgo to insert the corresponding rectangles and just connected the $2$-arrows to the sinks of the corresponding subquivers. It can be seen that this is no restriction from the combinatorial point of view.

We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$. If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, it is straightforward to get a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
Now we can recursively the $2$-quivers of $P_m^{(k)}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating this procedure. For $m\geq 4$, the truncated preprojective $\tau P_m^{(k)}$ can uniquely be found as a quotient of $P_m$.
Recall that we have $\udim P_m^{(k)}=\udim P_{m-1}^{(1)}+(n-k-1)\udim P_{m-1}$. Moreover, we have 
\[\dim \Hom(P_{m-1},\tau P_m^{(1)})=\dim\Ext(P_m^{(1)},P_{m-1})=n-1.\]

@@

\begin{tikzpicture}[scale=1]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
\draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
\draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
\node (Q0)[draw=black,fit={(I3) (J31) }]{};
\node (Q1)[draw=black,fit={(Q0) (J33)}]{};
\node (Q2)[draw=black,fit={(Q1) (I2) (J21) (J22) (J23)}]{};

@@

\draw (0,-4) node (I1b) {$\bullet$} +(1,1) node (J11b) {$\bullet$} +(1,0) node (J12b) {$\bullet$} +(1,-1) node (J13b) {$\bullet$}; 
\draw[->] (I1b)--(J11b) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I1b)--(J12b) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I1b)--(J13b) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};
